\begin{center}
  \large\textbf{ABSTRACT}
\end{center}

\addcontentsline{toc}{chapter}{ABSTRACT}

\vspace{2ex}

\begingroup
% Menghilangkan padding
\setlength{\tabcolsep}{0pt}

\noindent
\begin{tabularx}{\textwidth}{l >{\centering}m{3em} X}
  \emph{Name}     & : & \name{}         \\

  \emph{Title}    & : & \engtatitle{}   \\

  \emph{Advisors} & : & 1. \advisor{}   \\
                  &   & 2. \coadvisor{} \\
\end{tabularx}
\endgroup

% Ubah paragraf berikut dengan abstrak dari tugas akhir dalam Bahasa Inggris
\emph{This research presents a new approach to enhance mobility for ALS patients by developing a wheelchair movement control system using CNN (Convolutional Neural Network), which focuses on eye movement recognition, and is implemented on the Intel NUC platform. The study is driven by the challenges faced by ALS patients, who, despite losing physical mobility, can still move their eyes. The proposed system aims to provide greater independence and improved quality of life for these individuals. The research methodology consists of several key components: eye image capture and processing, extraction of relevant features, eye position estimation and classification, and control system execution on the Next Unit of Computing (NUC). By utilizing MediaPipe for real-time pose recognition and the computational capabilities of the Intel NUC, this study promises significant improvements in the autonomy of wheelchair users with mobility impairments. The classification model shows excellent performance based on the evaluation results of the confusion matrix, with accuracy, precision, recall, and F-1 score of 100\%. The model's performance remains stable at distances of 30 to 90 cm, with the highest accuracy at 30 and 50 cm (100\%) and under various lighting levels, with the highest accuracy at 131 Lux (100\%). The system maintains stable FPS on both a laptop and Intel NUC, showing better performance on the laptop. The average motor response time for the "Right," "Left," and "Reverse" commands is under 0.25 seconds, while for the "Forward" and "Stop" commands, it is about 0.43 seconds. The wheelchair motor shows consistent output time for each command class, with the lowest standard deviation on the "Forward" command (0.117), indicating the system's reliability in providing stable and consistent responses. This research not only contributes to the field of assistive technology but also has the potential to become a model for future innovations in mobility solutions for individuals with various physical disabilities.}

% Ubah kata-kata berikut dengan kata kunci dari tugas akhir dalam Bahasa Inggris
\emph{Keywords}: \emph{Assistive Technology, Gesture Recognition, Wheelchair Control, CNN, MediaPipe}